Alex's Notes and Text Fragments for the JSS Manuscript

### 2021-09-18 paper/paper.Rmd
resolve some comments

<!-- AB: TODO: folds = 5 makes very little sense in the case of LODO-CV, since this would only sample 5 discs, which cover only a small fraction of the study area. Let's use folds = 100, this will at least make readers think about their choice of #folds. -->

@@

<!-- TODO: AB: This diagram is inconsistent with the other diagrams - should display training and test samples. -->
```{r custom-cv-non-eval, eval=FALSE}
breaks = quantile(task$data()$dem, seq(0, 1, length = 6))
zclass = cut(task$data()$dem, breaks, include.lowest = TRUE)

@@

<!-- AB: TODO: The comment says that b$hash is optional, but the reader will not know what it is good for. A more verbose comment would be helpful, maybe 'optional task identifier' or whatever the hash name may be good for. -->
```{r create-task}
b = mlr3::as_data_backend(ecuador)
b$hash = "_mlr3_tasks_ecuador_" # optional
task = TaskClassifST$new(
  id = "ecuador", b, target = "slides", positive = "TRUE",
  extra_args = list(
    coordinate_names = c("x", "y"), coords_as_features = FALSE,
    crs = "EPSG:32717")
)
```

>>>>

@@

```{r custom-cv-non-eval, eval=FALSE}
breaks = quantile(task$data()$dem, seq(0, 1, length = 6))
zclass = cut(task$data()$dem, breaks, include.lowest = TRUE)

@@

```{r create-task}
b = mlr3::as_data_backend(ecuador)
task = TaskClassifST$new(
  id = "ecuador", b, target = "slides", positive = "TRUE",
  extra_args = list(
    coordinate_names = c("x", "y"), coords_as_features = FALSE,
    crs = "EPSG:32717")
)
```
